% PLAIN FILE TO HAVE REFERENCES FOR COMBUSTION AND FLAME
% STYLE
\def\rtn{\par \noindent}
\def\pskip{\rtn}

%%%%% A %%%%%%%
\def\aa{ Acta Astronautica}
\def\ab{ Acta Biomaterialia}
\def\abc{ Anal. Bioanal. Chem.}
\def\aam{ Adv. Appl. Mech.}
\def\aas{ Atomization and Sprays}
\def\abe{ Ann. of Biomed. Eng.}
\def\ag{ Adv. Geophys.}
\def\ats{ Ann. of Thora. Surg.}
\def\aiaaj{ Am. Inst. Aeronaut. Astronaut. J.}
\def\aiaap{ AIAA Paper}
\def\aj{ AIAA J.}
\def\ajou{ Aeronaut. J.}
\def\aicej{ AChE. J.}
\def\ajp{ Am. J. Phys.} 
\def\ana{ Anesth. Analg.}
\def\am{ App. Math.}
\def\amic{ App. Microbio.}
\def\an{ Acta Num.}
\def\anchem{ Anal. Chem.}
\def\anm{App.Num. Math.}
\def\ao{Artif. Organs}
\def\ap{ Adv. Phys.}
\def\apl{ App. Phys. Lett.}
\def\arbbs{ Ann. Rev. Biophys. Biomol. Struct.}
\def\arbe{ Ann. Rev. Biomed. Eng.}
\def\arfm{ Ann. Rev. Fluid Mech.}
\def\arp{ Ann. Rev. of Phys.}
\def\asas{ Astron. and Astrophys.}
\def\asaio{ Am. Soc. Artif. Intern. Org. }
\def\autcf{Reprinted by permission of Elsevier Science from}
\def\autcff{\copyright ~the Combustion Institute}
\def\autjfm{Reprinted with permission by Cambridge University Press}
\def\at{Atom. Sprays}
\def\atvb{ Arterioscl. Throm. Vas.}
\def\ajphcp{ Am. J. Physiol. Heart Circ. Physiol.}

%%%%% B %%%%%%%
\def\bioc{ Biochemistry-US}
\def\biom{ Biomat.}
\def\bb{ Biotechnol. Bioeng.}
\def\bba{ Biochim. Biophys. Acta}
\def\bbpc{ Ber. Bunsenges. Phys. Chem.}
\def\bioe{ Bioelectrochem.}
\def\bioee{ Bioelectro. Bioenerg.}
\def\biomat{ Biomaterials}
\def\biom{ Biomed. Mater.}
\def\biomf{ Biomicrofluid.}
\def\biomic{ Biomed. Microdev.}
\def\biop{ Biophys. J.}
\def\bior{ Biorheo.}
\def\bios{ Biosens. Bioelec.}
\def\blood{ Blood}
\def\blre{ Bl. Rev.}
\def\bmb{ Bull. Math. Biol.}
\def\bmm{ Biomech. Model. Mechanobiol.}

%%%%% C %%%%%%%
\def\canm{ Comm. Appl. Num. Meth.}
\def\care{ Cardiov. Res.}
\def\ccp{ Commun. Comput. Phys.}
\def\cea{ Cell Anal.}
\def\cepp{ Clin. Exp. Pharm. Phys.} 
\def\ces{ Chem. Eng. Sci.}
\def\cf{ Combust. Flame}
\def\cfl{ Comput. Fluids}
\def\cg{ Comput. Graph.}
\def\ch{ Chaos}
\def\cip{ Comput. Phys.}
\def\cir{ Cardiov. Interv. Radiol.}
\def\cire{ Circ. Res.}
\def\clch{ Clin. Chem.}
\def\clhem{ Clin. Hemorheo.}
\def\clm{ Clin. Lab. Med.}
\def\cm{ Comput. Mech.}
\def\cma{ Comput. Math. Appl.}
\def\cmame{ Comput. Meth. Appl. Mech. Eng.}
\def\cmb{ Cell. Mol. Bioeng.}
\def\cmmm{ Comput. Math. Meth. Med.}
\def\cmbbe{ Comput. Meth. Biomech. Biomed. Eng.}
\def\cocis{ Curr. Op. Coll. \& Interf. Sc.}
\def\cosuA{ Coll. Surf. A: Physicochem. Eng. Asp.}
\def\ca{ CA Cancer J. Clin.}
\def\cpa{ Cytom. Part A}
\def\cpam{ Commun. Pure Appl. Math.}
\def\cpc{ Computer Phys. Communications}
\def\cps{ Colloid Polym. Sci.}
\def\cras{ C. R. Acad. Sci.}
\def\crm{ Comp. Rend. M\'ec.}
\def\crp{ Comp. Rend. Phys.}
\def\cs{ Comput. Struct.}
\def\cst{ Combust. Sci. Tech.}
\def\ctm{ Combust. Theory and Modelling}
\def\cve{ Cardiov. Eng.}
\def\cvet{ Cardiov. Eng. Tech.}
\def\cvs{ Comput. Visual. Sci.}
\def\spctr{ Proc. of the Summer Program, Stanford NASA C.T.R}
\def\ctrarb{ Ann. Res. Briefs}
\def\cyto{ Cytotech.}

%%%%% D %%%%%%%
\def\diab{ Diabetes}
\def\ddt{ Dru. Disc. Tod.}
\def\DHCRS{ Dynamics of Heterogeneous Combustion and Reacting Systems}

%%%%% E %%%%%%%
\def\eacfm{ Eng. Appl. Comp. Fluid}
\def\ebj{ Eur. Biophys. J.}
\def\ejam{ Eur. J. of App. Math.}
\def\elp{ Electrophoresis}
\def\emman{ ESAIM: Math. Mod. Num. Anal.}
\def\ent{ Entropie}
\def\ep{ ESAIM: Proc.}
\def\epjb{ Eur. Phys. J. B}
\def\epje{ Eur. Phys. J. E}
\def\epl{ Europhys. Lett.}
\def\ermd{ Exp. Rev. Med. Dev.}
\def\etme{ Eng. Turb. Mod. and Exp.} 
\def\eurad{ Eur. Radiol.}
\def\exf{ Exp. Fluids}
\def\ejcs{ Eur. J. Cardio-thorac.}
\def\ehj{ Eur. Heart J.}

%%%%% F %%%%%%%
\def\fd{ J. Fluid Dynamics}
\def\fdr{ Fluid Dyn. Res.}
\def\fead{ Finite Elem. Anal. Des.}
\def\ftc{ Flow, Turb. and Combustion}
\def\fp{ Front. Physiol.}

%%%%% I %%%%%%%
\def\icvts{ Interact. CardioVasc. Thorac. Surg.}
\def\icmf{ Int. Conf. Multiphase Flow}
\def\iecf{ Ind. Eng. Chem. Fundam.}
\def\ija{ Int. J. Aeroacous.}
\def\ijam{ Int. J. of Appl. Mech.} 
\def\ijao{ Int. J. Artif. Organs}
\def\ijav{ Int. J. Acoust. Vib.}
\def\ijcfd{ Int. J. Comput. Fluid Dyn.}
\def\ijcm{ Int. J. Comput. Meth.}
\def\ijhff{ Int. J. Heat Fluid Flow}
\def\ijiee{ Int. J. Info. Elec. Eng.}
\def\ijlh{ Int. J. Lab. Hemat.}
\def\ijmav{ Int. J. Micro Air Veh.}
\def\ijmf{ Int. J. Multiph. Flow}
\def\ijmp{ Int. J. Modern Phys. C}
\def\ijnmbe{ Int. J. Numer. Meth. Biomed. Eng.}
\def\ijnme{ Int. J. Numer. Meth. Eng.}
\def\ijnmf{ Int. J.~Numer. Meth. Fluids}
\def\ijhmt{ Int. J.~Heat and Mass Trans.}
\def\ijts{ Int. J. of Therm. Sci.}
\def\inc{ Il Nuovo Cimento}
\def\infoc{ Interf. Focus}
\def\irsnc{ IRSN Cardiol.}
\def\irsnr{ IRSN Radiol.}
\def\itps{ IEEE Trans. Plasma Sci.}
\def\iembm{ IEEE Eng. Med. Biol. Mag.}

%%%%% J %%%%%%%

\def\ja{ J. Aircraft}
\def\jacc{ J. Am. Coll. Cardio.}
\def\jacic{ J. Aeropace Comput. Inform. Comm.}
\def\jaes{ J. Aeronaut. Sci.}
\def\jala{ J. Lab. Autom.}
\def\jame{ J. Appl. Mech.}
\def\jap{ J. Appl. Phys.}
\def\japgy{ J. Appl. Physiol.}
\def\jars{ J.~Am. Rocket Soc.}
\def\jas{ J. Atmos. Sci.}
\def\jasa{ J. Acous. Soc. Am.}
\def\jawma{ J. Air Waste Manag. Assoc.}
\def\jchp{ J. Chem. Phys.}
\def\jb{ J. Biomech.}
\def\jbc{ J. Biol. Chem.}
\def\jbe{ J. Biomech. Eng.}
\def\jbmr{ J. Biomed. Mat. Res. }
\def\jcam{ J. Comput. Appl. Math.}
\def\jcht{ J. Chem. Thermodyn.}
\def\jcis{ J. Coll. Interf. Sci.} 
\def\jcp{ J.~Comput. Phys.}
\def\jcsft{ J. Chem. Soc., Faraday Trans. 2}
\def\je{ J. Energy}
\def\jegtp{ J. Eng. Gas Turb. Power}
\def\jem{ J. Emerg. Med.}
\def\jep{ J. Eng. Power}
\def\jfe{ J. Fluids Eng.}
\def\jfm{ J.~Fluid Mech.}
\def\jfs{ J. Fluids Struct.}
\def \jhc{ J. Histochem. Cytochem.} 
\def\jhlt{ J. Heart Long Transplant.}
\def\jhvd{ J. Heart Valve Dis.}
\def\jht{ J. Heat Trans.}
\def\jhmt{ J. Heat Mass Trans.}
\def\jie{ J. Inst. Energy}
\def\jjap{ Jap. J. Appl. Phys.}
\def\jmfm{ J. Math. Fluid Mech.}
\def\jm{ J. M\'ec.}
\def\jmb{ J. Math. Biol.}
\def\jmbbm{ J. Mech. Behav. Biomed.}
\def\jmm{ J. Micromech. Microeng.}
\def\jmmb{ J. Mech. Med. Biol.}
\def\jmps{ J. Mech. Phys. Sol.}
\def\jmta{ J. M\'ec. Th\'eor. Appl.}
\def\jnc{ J. Neurocyto.}
\def\jncs{ J. Non-Cryst. Sol.}
\def\jnnfm{ J. Non-Newt. Fluid Mech.}
\def\jtb{J. Theor. Biol.}
\def\jtm{J. Theor. Med.}
\def\jotu{ J.~Turb.}
\def\jpamg{ J. Phys. A: Math. Gen.}
\def\jpcm{ J. Phys.: Condens. Matter}
\def\jpcs{ J. Phys.: Conf. Series}
\def\jpdap{ J. Phys. D: Appl. Phys.}
\def\jpp{ J.~Prop.~Power}
\def\jpr{ J. Plank. Res.}
\def\jrnbs{ J. Res. Natl. Bur. Stand.}
\def\jrsif{ J. R. Soc. Interf.}
\def\jsaed{ J. Strain Anal. Eng. Des.}
\def\jsc{ J. Sci. Comput.}
\def\jsp{ J. Stat. Phys.}
\def\jsr{ J. Spacecrafts and Rockets}
\def\jsv{ J.~Sound Vib.}
\def\jssc{ SIAM J. Sci. Stat. Comput.}
\def\jt{ J.~Turb.}
\def\jtcs{ J.~Thorac. Cardiovasc. Surg.}
\def\jtht{ J. Thermophys. and Heat Trans.}
\def\jth{ J. Thromb. Haemost.} 
\def\jtt{ J. Thromb. Thrombol.}
\def\jtu{ J. Turbomach.}

%%%%% L %%%%%%%
\def\labc{ Lab. Chip}
\def\lifes{ Life Sci.}
\def\lanl{ LANL Tech. Rep.}

%%%%% M %%%%%%%
\def\mbs{ Math. Biosci.}
\def\mc{ Microcirc.}
\def\mcb{ Mech. Chem. Biosys.}
\def\mcm{ Math. Comput. Mod.}
\def\mep{ Med. Eng. Phys.}
\def\micnan{ Microfluid. Nanofluid.}
\def\miceng{ Microelec. Eng.}
\def\mmb{ Math. Med. Biol.}
\def\mmmas{ Math. Mod. Meth. App. Sc.}
\def\moc{ Math. Comp.}
\def\mr{ Microv. Res.}
\def\msbec{ Mat. Sci. Eng. C}
\def\mst{ Meas. Sci. Technol.}
\def\mwr{ Mon. Weather Rev.}

%%%%% N %%%%%%%
\def\nano{ Nano Today}
\def\nat{ Nature}
\def\natmed{ Nat. Med.}
\def\ned{ Nuclear Eng. and Design}
\def\njop{ New J. Phys.}
\def\nephr{Nephrology}
\def\nrc{ Nat. Rev. Cardiol.}
\def\nejm{ New Eng. J. Med.}

%%%%% O %%%%%%%
\def\ogst{ Oil Gas Sci. Tech.}

%%%%% P %%%%%%%
\def\paa{ Prog. Astr. Aero.}
\def\pas{ Prog. Aerospace Sci.}
\def\pbmb{ Prog. Biophys. Mol. Biol.}
\def\pcfd{ Prog. Comput. Fluid Dyn.}
\def\pci{ Proc. Combust. Inst.}
\def\pcp{ Prog. Comput. Phys.}
\def\pecs{ Prog. Energy Comb. Sci.}
\def\pf{ Phys. Fluids}
\def\pht{ Pathophysiol. Haemost. Thromb.}
\def\physd{ Physica D}
\def\pime{ Proc. Instn. Mech. Engrs.}
\def\plms{ Proc. London Math. Soc}
\def\plos{ PLoS One}
\def\ploscb{ PLoS Comp. Biol.}
\def\pmb{ Phys. Med. Biol.}
\def\pnas{ Proc. Natl Acad. Sc. USA}
\def\ppc{ Prog. Ped. Cardio.}
\def\pps{ Prog. Polym. Sci.}
\def\ppsc{ Part. Part. Syst. Charact.}
\def\pra{ Phys. Rev. A}
\def\pre{ Phys. Rev. E}
\def\prl{ Phys. Rev. Lett.}
\def\prsl{ Proc. R. Soc. Lond.}
\def\prsla{ Proc. R. Soc. Lond. A}
\def\prslb{ Proc. R. Soc. Lond. B}
\def\pt{ Powder Technology}
\def\prsa{ Proc. R. Soc. A}
\def\perf{ Perfusion}
\def\ptrsb{ Phil. Trans. R. Soc. B}

%%%%% Q %%%%%%%
\def\qjmam{ Q. J. Mech. Appl. Math.}

%%%%% R %%%%%%%
\def\ra{ La Rech. A\'{e}rospatiale}
\def\rct{ Rubber Chem. Technol.}
\def\rhac{ Rheol. Acta}
\def\rrcc{ Res. Rep. Clin. Cardio.}
\def\rpa{ Rev. Phys. Appl.}

%%%%% S %%%%%%%
\def\sbm{ WIREs Syst. Biol. Med.}
\def\sci{ Science}
\def\screp{ Sc. Rep.}
\def\sab{ Sens. Act. B}
\def\sjam{ SIAM J. Appl. Math.}
\def\sjna{ SIAM J. Num. Anal.}
\def\sjsc{ SIAM J. Sci. Comput.}
\def\sm{ Soft Mat.}
\def\sth{ Semin. Thromb. Hemost.}
\def\stm{ Sci. Transl. Med.}

%%%%% T %%%%%%%
\def\tcfd{ Theoret. Comput. Fluid Dyn.}
\def\tcsme{ ASME Trans.}
\def\ti{ Technique de l'Ing\'enieur}
\def\thc{ Tech. Health Care}
\def\tjms{ Turk. J. Med. Sci.}
\def\tsfp{ Turb. Shear Flow Phen.}
\def\tr{ Thromb. Res.}
\def\tajp{ Am. J. Pathol.}


%%%%% W %%%%%%%
\def\WSSCI{ WSS/CI}

\def\Litem{\par\noindent}
\font\smc=cmcsc10
